The Social Conditioning of Fear

### 2023-12-06 scripts/manuscript.qmd
some fear of crime lit

---
title: "The Social Conditioning of Fear"
author:
  - Alejandra Pedraza
  - W. Jamie Yang
abstract: "TBW" # this is where abstract should be pasted 
format: html
toc: true
toc-location: left
toc-title: Table of Contents
highlight-style: pygments
editor: visual
execute:
  eval: true # change to false before final submission
  echo: true
  message: false
  warning: false
fig-width: 6.5
fig-height: 8
code-fold: true
code-summary: "View Code"
embed-resources: true
bibliography: references.bib
link-citations: true
---

@@

I'm leaving myself a note here to figure out how to do word count in a Quarto document. This will allow me to directly write in the qmd file and save the trouble of writing elsewhere like a word document and pasting things here.

>>>>

---
title: "The Social Conditioning of Fear"
author:
  - Alejandra Pedraza
  - W. Jamie Yang
abstract: "TBW" # this is where abstract should be pasted 
format: html
    wordcount-html: default
toc: true
toc-location: left
toc-title: Table of Contents
highlight-style: pygments
editor: visual
execute:
  eval: true # change to false before final submission
  echo: true
  message: false
  warning: false
fig-width: 6.5
fig-height: 8
code-fold: true
code-summary: "View Code"
embed-resources: true
bibliography: references.bib
link-citations: true
---

@@

This is an exploratory project for a dissertation chapter idea that one of the co-authors wants to pursue. With descriptive statistics, we are interested in investigating the inequalities in terms of fear of walking alone at night among US adult population and mapping out the patterns of disparities along the axes of race, gender, sexual orientation, citizenship status, and education.

Individuals' report of fear have been shown to relate to a wide range of contextual factors, such as neighborhood composition and community crime rates [@hale1996; @warr1990], and individual sociodemographic characteristics, such as gender, sexual orientation, income, age, health condition, and immigration status [@lagrange1989; @otis2007; @madriz2023].

Especially, the role of gender in fear of crime has been well documented in victimization research [@stanko1993; @snedker2006; @schnitzer2010].
